SPARQL on the open, decentralised Web

### 2016-06-03 dissertation/papersincontext.tex
add label
make todos visible

\section{The papers in context}

@@

%TODO: not the Dagstuhl?
% TODO: relate to problems
This paper is relevant to the topic of the dissertation for two
reasons: First, it shows how hypermedia may be used to drive a
read-write application, not just read-only, which is the focus of most
of the discussion. Second, it provides some of the basis for
\cite{ldf1}, which is important in the query planner.

>>>>

\section{The papers in context}\label{sec:papersincontext}

@@

\todo{not the Dagstuhl?}
\todo{relate to problems}
This paper is relevant to the topic of the dissertation for two
reasons: First, it shows how hypermedia may be used to drive a
read-write application, not just read-only, which is the focus of most
of the discussion. Second, it provides some of the basis for
\cite{ldf1}, which is important in the query planner.
